DraftFunctions

### 2022-02-04 R/DraftFunctions.Rmd

>>>>

# Generate prospection units
```{r}
HarvestableAreaOutputsCable <- harvestableareadefinition(
  topography = DTMParacou,
  creekdistances = CreekDistances,
  maintrails = MainTrails,
  plotmask = PlotMask,
  scenario = "manual", winching = "1",
  advancedloggingparameters = loggingparameters()
)

# usethis::use_data(HarvestableAreaOutputsCable, overwrite = TRUE)
```
